---
title: "Day 4 - Passport Processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(data.table)
library(readr)
library(stringr)
library(purrr)
library(tidyverse)
```

Has to have: 

- byr (Birth Year)
- iyr (Issue Year)
- eyr (Expiration Year)
- hgt (Height)
- hcl (Hair Color)
- ecl (Eye Color)
- pid (Passport ID)
- cid (Country ID) (optional)

```{r}
data <- read_file("../data/Day4.txt")
data <- str_split(data, "\n\n")
data <- as.list(data[[1]])
data <- map(data, str_split, "\n", simplify=TRUE)
data <- map(data, strsplit, " ")
data <- lapply(data, unlist)
```

```{r}
fields_obligatory <- c("byr", "iyr", "eyr", "hgt", "hcl", "ecl", "pid")
count <- map(data, ~str_count(.x,paste(fields_obligatory, collapse='|')))
count2 <- map(count, sum)

data2 <- list()
valid_counter <- 0
for(i in seq_along(count2)){
  if(count2[[i]]==7){
    valid_counter <- valid_counter+1
    data2[[valid_counter]] <- data[[i]]
  }
}
valid_counter
```

## Part 2

```{r}
data2 <- map(data2, str_split, ":")
```

```{r}
value <- map(data2, ~map(.x, 2) %>% unlist())
names <- map(data2, ~map(.x,1) %>%  unlist())
named_values <- map2(value, names, ~`names<-`(.x,.y))
```

```{r}
data2 <- bind_rows(named_values)
```

```{r}
rm(list=setdiff(ls(), "data2"))
```



Conditions to test: 

- iyr (Issue Year) - four digits; at least 2010 and at most 2020.

```{r}
data2$iyr <- as.integer(data2$iyr)
validation <- data.frame(iyr=data2$iyr>=2010 & data2$iyr<=2020)
```

- ecl (Eye Color) - exactly one of: amb blu brn gry grn hzl oth.

```{r}
ecl <- c("amb", "blu", "brn", "gry", "grn", "hzl", "oth")
validation$ecl <- data2$ecl %in% ecl
```

- hgt (Height) - a number followed by either cm or in:
  - If cm, the number must be at least 150 and at most 193.
  - If in, the number must be at least 59 and at most 76.
  
```{r}
data2$height_num <- gsub("[^[:digit:]]", "", data2$hgt) %>% as.integer()
data2$height_unit <- gsub("[[:digit:]]", "", data2$hgt) 


for(i in seq_along(data2$height_unit)){
  validation$hgt[i] <- if(data2$height_unit[i]=="cm"){
    data2$height_num[i]>=150 & data2$height_num[i]<=193
  }else{
    data2$height_num[i]>=59 & data2$height_num[i]<=76
  }
}  
```
  
- pid (Passport ID) - a nine-digit number, including leading zeroes.

```{r}
validation$pid <- map_lgl(data2$pid, ~str_count(.x, paste(0:9, collapse='|'))==9)
```

- byr (Birth Year) - four digits; at least 1920 and at most 2002.

```{r}
data2$byr <- as.integer(data2$byr)
validation$byr <- data2$byr>=1920 & data2$byr<=2002
```

- hcl (Hair Color) - a # followed by exactly six characters 0-9 or a-f.

```{r}

x <- logical()
for(i in seq_along(data2$hcl)){
    if(substr(data2$hcl[i], 1,1)=="#"){
  x[i] <- nchar(substr(data2$hcl[i], 2,7))==6 & str_count(substr(data2$hcl[i], 2,7), paste(c(letters, 0:9), collapse = '|'))==6
} else x[i] <- FALSE
  }
  
validation$hcl <- x
```

- eyr (Expiration Year) - four digits; at least 2020 and at most 2030.

```{r}
data2$eyr <- as.integer(data2$eyr)
validation$eyr <- data2$eyr>=2020 & data2$eyr<=2030
```

- cid (Country ID) - ignored, missing or not.

```{r}
y <- logical()

for(i in 1:nrow(validation)){
   x <- as.logical(validation[i,]) %>% all()
   y <- c(y,x)
}

validation$all_TRUE <- y
table(y)
```





